A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-20 tex/body.tex
more

CVC4 was run on each problem several times, with the support for datatypes and
codatatypes either enabled or disabled. The contributions of the acyclicity and
uniqueness rules were also measured, to find out whether these somewhat
expensive rules are useful in practice. Even when the decision procedure is
disabled, some of the generated axioms typically include basic properties of
constructors and selectors, which the decision procedure would recognize as
tautologies. Z3 is included for comparison when this makes sense.
%This allows us to answer the question, \relax{What are the
%benefits of activating the decision procedure as opposed to letting
%Sledgehammer do what it would normally do?}

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all three benchmark suites. It accounts for an overall
success rate increase of over \OK{5\%}, which is quite significant. The
practical usefulness of interpreted (co)datatypes appears roughly comparable to
that of arithmetic \cite{blanchette-et-al-2013-smt}.
The raw data also reveals that the
stronger decision procedures almost completely subsume the weaker ones.

>>>>

The development version of CVC4 was run on each problem several times, with the
support for datatypes and codatatypes either enabled or disabled. The
contributions of the acyclicity and uniqueness rules were also measured, to find
out whether these somewhat expensive rules are useful in practice. Even when the
decision procedure is disabled, some of the generated axioms typically include
basic properties of constructors and selectors, which the decision procedure
would recognize as tautologies. Z3 version 4.3.2 is included for comparison.
% when this makes sense.
%This allows us to answer the question, \relax{What are the
%benefits of activating the decision procedure as opposed to letting
%Sledgehammer do what it would normally do?}

@@

The results are summarized in Table~\ref{tab:bench}. The decision procedure
makes a difference across all three benchmark suites. It accounts for an overall
success rate increase of over \OK{5\%}, which is quite significant. For Isabelle
users, the practical usefulness of interpreted (co)datatypes appears roughly
comparable to that of arithmetic \cite{blanchette-et-al-2013-smt}. The raw data
also reveals that the stronger decision procedures almost fully subsume the weaker
ones.
